### 2007-01-11 Documentation/appendix.tex
*** empty log message ***

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Catalogue of {\sf AEDL}-Files}
\label{app:aedlfiles}
Along with the \GLOBES\ package comes a catalogue of pre-defined experiment \AEDL\ files for different
future experiments and different beam and detector technologies. These include the planned superbeam experiments
and their possible upgrades, different reactor experiment setups, different $\beta$-beam setups, and different 
neutrino factory setups. A complete list
of all pre-defined experiment files an be found in \tabl{experiments}. More detailed descriptions of the
corresponding files, the assumptions, requirements, and references are given in the following.

\section*{Superbeam experiments}
\subsection*{T2K -- {\tt T2K.glb}}

The \TtoK\ experiment can be simulated with the file {\tt T2K.glb}. This file tries to approximate as closely as
possible the LOI \cite{Itow:2001ee} and the basic version was used within \cite{Huber:2002mx}. These references
should be cited if the file {\tt T2K.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt T2K.glb}, the following additional files are required: 
\bi
\item {\tt JHFplus.dat} (neutrino flux from J-PARC -- $\nu_\mu$)
\item {\tt JHFminus.dat} (neutrino flux from J-PARC -- $\bar{\nu}_\mu$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\item {\tt XQE.dat} (quasi elastic cross sections)
\ei
The \TtoK\ neutrino beam is produced at J-PARC and directed towards the Super-Kamiokande detector. The target
power is 0.77~MW and 2~years $\nu$-running and 6~years $\bar{\nu}$-running is assumed. The fiducial mass of the
Super-Kamiokande Water Cerenkov detector is taken to be $\mathrm{m_{det} = 2.5 \,kt}$ at a baseline of
L~=~295~km. The appearance measurement involves the total rates data from all CC events and the spectral data
from the QE sample with a free normalization at an energy resolution of $\mathrm{\sigma_e=0.085\, GeV}$ due to the
Fermi Motion as is described in more detail in~\cite{Huber:2002mx}. The treatment of systematics is similar to
\cite{Ishitsuka:2005qi}. The following rules are defined within {\tt T2K.glb}:  
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $0.9 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{QE}}$ & & 0.025 & $10^{-4}$\\
 & &  & &\\
Background & $0.0056 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+) -- Spectrum}  & & \\ \hline
Signal & $0.505 \, \otimes \, (\nu_\mu \rightarrow \nu_e)_\mathrm{QE}$ & & 10.0 & $10^{-4}$\\
 & & & & \\
Background & $0.0056 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $3.3\cdot 10^{-4} \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & 0.05 & 0.05\\
Beam background & $0.505 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$ & $0.505 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$  & 0.05 & 0.05\\ \hline \hline
\multicolumn{3}{|l|}{Appearance (+) -- Total Rates}  & & \\ \hline
Signal & $0.505 \, \otimes \, (\nu_\mu \rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & $10^{-4}$\\
 & & & & \\
Background & $0.0056 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $3.3\cdot 10^{-4} \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & 0.05 & $10^{-4}$\\
Beam background & $0.505 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$ & $0.505 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$  & 0.05 & $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} & & \\ \hline 
Signal & $0.9 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{QE}}$ & & 0.025 & $10^{-4}$\\
 & &  & &\\
Background & $0.0056 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--) -- Spectrum}  & & \\ \hline
Signal & $0.505 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e)_\mathrm{QE}$ & & 10.0 & $10^{-4}$\\
 & & & & \\
Background & $0.0056 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $3.3\cdot 10^{-4} \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & 0.05 & 0.05\\
Beam background & $0.505 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & $0.505 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$  & 0.05 & 0.05\\ \hline \hline
\multicolumn{3}{|l|}{Appearance (--) -- Total Rates}  & & \\ \hline
Signal & $0.505 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & $10^{-4}$\\
 & & & & \\
Background & $0.0056 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $3.3\cdot 10^{-4} \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & 0.05 & $10^{-4}$\\
Beam background & $0.505 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & $0.505 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$  & 0.05 & $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

\subsection*{T2HK -- {\tt T2HK.glb}}

\TtoHK\ is the superbeam upgrade of the \TtoK\ experiment and can be simulated with the file {\tt T2HK.glb}. 
The target power is 4~MW and 
4~years $\nu$-running and 4~years $\bar{\nu}$-running is assumed.
The fiducial mass of the Water Cerenkov detector is taken to be $\mathrm{m_{det} = 500 \,kt}$ at the same
baseline as the \TtoK\ experiment. Besides these changes, the file {\tt T2HK.glb} is similar to {\tt T2K.glb}
and the same additional files are required. 
The basic version was used within \cite{Huber:2002mx} which should be cited if the file {\tt T2K.glb} is 
used for a scientific publication or a talk.

\subsection*{NO$\nu$A -- {\tt NOvA.glb}}

The \NOVA\ experiment can be simulated with the file {\tt NOvA.glb}. The description of the disapperance 
channels is taken from \cite{Yang_2004} and the description of the appearance channels follows 
the proposal \cite{Ambats:2004js}. These references
should be cited if the file {\tt NOvA.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt NOvA.glb}, the following additional files are required: 
\bi
\item {\tt NOvAplus.dat} (NuMI neutrino flux -- $\nu_\mu$)
\item {\tt NOvAminus.dat} (NuMI neutrino flux -- $\bar{\nu}_\mu$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The \NOVA\ experiment uses a neutrino beam from the Fermilab NuMI beamline. The target power is 
1.2~MV which results in $10^{21}$~pot~$\mathrm{yr^{-1}}$ and 3~years $\nu$-running and 3~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Totally Liquid Scintillator Detector (TASD) is taken to be 
$\mathrm{m_{det} = 25 \,kt}$ at a baseline of L~=~812~km approximately 12~km off-axis to the beamline. The
energy resolution is $\mathrm{\sigma_e=10 \% \cdot \sqrt{E}}$ for electrons and  $\mathrm{\sigma_e=5 \% \cdot \sqrt{E}}$
for muons. The following rules are defined within {\tt NOvA.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.8 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} & & \\ \hline
Signal & $0.24 \, \otimes \, (\nu_\mu \rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} &  &  \\ \hline
Signal & $0.8 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} & & \\ \hline
Signal & $0.37 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0037 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\end{tabular}
\end{center}

\subsection*{SPL - {\tt SPL.glb}}

The \SPL\ experiment can be simulated with the file {\tt SPL.glb}. This file was used in \cite{Campagne:2006yx}
and follows the experiment description from \cite{Mezzetto:2003mm, Campagne:2004wt}. These references
should be cited if the file {\tt SPL.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt SPL.glb}, the following additional files are required: 
\bi
\item {\tt SPLplus.dat} (neutrino flux from CERN -- $\nu_\mu$)
\item {\tt SPLminus.dat} (neutrino flux from CERN -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_spl.dat} (charged current cross sections)
\item {\tt XNC\_spl.dat} (neutral current cross sections)
\ei
The \SPL\ experiment uses a neutrino beam from the CERN to Fr\'{e}jus. The target power is 
4~MV and 2~years $\nu$-running and 8~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Water Cerenkov detector is taken to be 
$\mathrm{m_{det} = 500 \,kt}$ at a baseline of L~=~130~km. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describe energy smearing mainly
from Fermi Motion. The following rules are defined within {\tt SPL.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} &  & \\ \hline
Signal & $0.707 \, \otimes \, (\nu_\mu\rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $6.5\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} & & \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} &  & \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_\mu\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $0.0025 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\nu_\mu \rightarrow \nu_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

\section*{Reactor experiments}
\subsection*{Small reactor experiment -- {\tt Reactor1.glb}}

The file {\tt Reactor1.glb} allows to simulate a small $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor1.glb} is
used for a scientific publication or a talk. For calculations that involve {\tt Reactor1.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The neutrino source is the core of a nuclear power reactor. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 400 \,t \, GW\, yr}$, \eg\ a 20~t detector, a reactor with a thermal power of 4~GW
and a running period of 5 years. As detector technology a liquid scintillator 
detector is assumed, a far detector at a baseline of L~=~1.7~km and a near detector which is
assumed to be identical to the far detector (maybe apart from the size) in order to minimize the impact of systematical uncertainties. The normalization error
used in the file {\tt Reactor1.glb} has to be considered as an effective error, receiving contributions from
individual uncertainties (see~\cite{Huber:2003pm}). The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Reactor1.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & \hspace{5.5cm} & 0.008 & 0.005\\
 & &  & &\\
Background & $5.8\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_\mathrm{CC}$ & \hspace{5.5cm} &
$10^{-6}$ & $10^{-6}$ \\ \hline \hline 
\end{tabular}
\end{center}

\subsection*{Large reactor experiment -- {\tt Reactor2.glb}}

The file {\tt Reactor2.glb} allows to simulate a large $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor2.glb} is
used for a scientific publication or a talk. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 8000 \,t \, GW\, yr}$, \eg\ a 100~t detector, a reactor with a thermal power of 10~GW
and a running period of 8 years. Besides the higher integrated luminosity, the attributes of {\tt Reactor2.glb}
are similar to the ones of {\tt Reactor1.glb}.

\subsection*{DoubleCHOOZ -- {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb}}

The files {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic version of these files were used within \cite{Huber:2006vr} which should be cited if the files 
{\tt Dchooz-near.glb} and {\tt Dchooz-far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt Dchooz-near.glb} and/or {\tt Dchooz-far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt Dchooz-near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

\section*{Beta beam experiments}
\subsection*{CERN-Fr\'{e}jus baseline scenario -- {\tt BB\_100.glb}}

The $\gamma=100$ $\beta$-beam baseline scenario from CERN to Fr\'{e}jus can be simulated with the file {\tt
BB\_100.glb}. The basic version of this file was used within \cite{Campagne:2006yx}. This reference
should be cited if the file {\tt BB\_100.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BB\_100.glb}, the following additional files are required: 
\bi
\item {\tt BB100flux\_Ne.dat} ($\beta$-beam neutrino flux -- $^{18}$Ne stored at $\gamma=100$)
\item {\tt BB100flux\_He.dat} ($\beta$-beam neutrino flux -- $^{6}$He stored at $\gamma=100$)
\item {\tt BeamBckg\_100.dat} (beam background)
\item {\tt AtmBckg\_100.dat} (atmospheric background)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_Nuance.dat} (charged current cross sections)
\item {\tt XNC\_Nuance.dat} (neutral current cross sections)
\item {\tt Null.dat} (auxiliary file)
\ei
The neutrino beam is produced at CERN and directed towards a a megaton Water Cerenkov detector at Fr\'{e}jus. 
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=100$ for both types of isotopes and $2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $5.8\cdot10^{18}$ $^{6}$He decays per year are assumed. The CERN-Fr\'{e}jus baseline is L~=~130~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describes energy smearing mainly
from Fermi Motion. The following rules are defined within {\tt BB\_100.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.707 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{CC}}$ & & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & (from external file) & 0.02 & $10^{-4}$ \\
Atm. background & & (from external file) & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e \rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (from external file) & 0.02 & $10^{-4}$ \\
Atm. background & & (from external file) & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

\subsection*{Higher gamma scenario -- {\tt BB\_350.glb}}

A $\gamma=350$ medium gamma $\beta$-beam green-field scenario involving a megaton Water Cerenkov detector can be simulated with the file {\tt
BB\_350.glb}. This file tries to approximate as closely as possible the scenario {\sf Setup III} from
\cite{Burguet-Castell:2005pa}. This reference
should be cited if the file {\tt BB\_350.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BB\_350.glb}, the following additional files are required: 
\bi
\item {\tt BB350flux.dat} ($\beta$-beam neutrino flux -- $\gamma=350$ )
\item {\tt NeEffMig350.dat} (migration matrix -- $\nu_\mu$)
\item {\tt NeBckgRej350.dat} (migration matrix -- background)
\item {\tt NeDisEff350.dat} (migration matrix -- $\nu_e$)
\item {\tt HeEffMig350.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt HeBckgRej350.dat} (migration matrix -- background)
\item {\tt HeDisEff350.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=350$ for both types of isotopes and $2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $5.8\cdot10^{18}$ $^{6}$He decays per year are assumed. The baseline is L~=~730~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The energy resolution is introduced manually by
six migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$, and the background from NC events
for $^{18}$Ne and $^6$He) that describes energy smearing. These migration matrices also already include energy
dependend efficiencies and background rejection factors. They are taken from the appendix of
\cite{Burguet-Castell:2005pa}. The following rules are defined within {\tt BB\_350.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{CC}}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & neglected & (systematic uncertainty dominates) & -- & -- \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & (migration matrix) & 0.05 & $10^{-4}$
\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & neglected & (systematic uncertainty dominates) & -- & -- \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & (migration matrix)  &
0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (migration matrix) & 0.05 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

\subsection*{Variable beta beam (Water Cerenkov) -- {\tt BBvar\_WC.glb}}
